---
title: "Predictive Wavelength Switching Project"
author: "Zahra Bakhtiari, Sergey Samsonau"
date: "October, 2016"
output: html_document
---
```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, eval = T, warning = F)
```

Loading libraries

```{r}
library(stringr); library(dplyr); library(readxl); library(gtools); library(ggplot2)
```

# The Goal

Predict the value of the gain at other channels by having few input channels. This code provides the best wavelength choices for several-add events with pre-existing channels supplied in Input file

## Script Parameters

Following parameter defines the number of newly added wavelengths

```{r}
num_add_wl <- 3
```

Next parameter defines the gap for divergence of power between ripples, the ideal value is 0.

```{r}
m_pre = 0.08 # margin for pre_ext
m_new = m_pre # margin for new
```


## Data Preparation

### Location, names, structure of the files with data

There are two files specified:

* file with fully loaded bands
* Input file with initial numbe of bands loaded 

```{r}
# Give the values
# * directory with data
data_dir_path <- "./data/"
# * name of the file with fully loaded bands
FLB_filename <- "Fully Loaded Band.xlsx"
# * name of the file with Input
Input_filename <- "Input.xlsx"
# * names of coloumns in files
col_names <- c("Freq", "wl", "PowerIn", "PowerOut", "Gain")
```

### Reading data

```{r data}
if(exists("tb_Total")) rm(tb_Total)
# read fully loaded bands file
tb_FLB <- read_excel(str_c(data_dir_path, FLB_filename), skip = 1)
names(tb_FLB) <- col_names

if(exists("tb_Input")) rm(tb_Input)
# read input file
tb_Input <- read_excel(str_c(data_dir_path, Input_filename), skip = 1)
names(tb_Input) <- col_names
```

How many distinct frequencies in the loaded data

```{r}
# full load bands
num_FLB <- length(unique(tb_FLB$Freq))
num_FLB
# input bands
num_Input <- length(unique(tb_Input$Freq))
num_Input
```

### create IDs for frequencies

```{r}
freq_map <- select(tb_FLB, Freq) %>%
  arrange(Freq) %>%
  mutate(freq_text_id = str_c("g_", str_pad(1:num_FLB, 2, pad = "0")),
         freq_num_id = str_pad(1:num_FLB, 2, pad = "0")) # as.numeric

# checking
freq_map
```

Add frequency IDs to corresponding places. Also add column containing data type.

```{r}
tb_FLB <- tb_FLB %>%
  full_join(freq_map) %>%
  mutate(data_type = "Full load") %>%
  arrange(freq_num_id)

tb_FLB

tb_Input <- tb_Input %>%
  full_join(freq_map) %>%
  mutate(data_type = "Input") %>%
  arrange(freq_num_id)
  
tb_Input
tb_Input %>% filter(! is.na(wl))
```

### Calculation of ratios

```{r}
# FLB
for (id in tb_FLB$freq_text_id) {
  root_gain <- filter(tb_FLB, freq_text_id == id) %>%
    select(Gain) %>% unlist()
  tb_FLB[, str_c(id, "_over")] <-
    (10 ^ (tb_FLB$Gain / 10)) / (10 ^ (root_gain / 10))
}

# Input
for (id in tb_Input$freq_text_id) {
  root_gain <- filter(tb_Input, freq_text_id == id) %>%
    select(Gain) %>% unlist()
  tb_Input[, str_c(id, "_over")] <-
    (10 ^ (tb_Input$Gain / 10)) / (10 ^ (root_gain / 10))
}
```

Combine both data sets in one tibble

```{r}
tb_Total <- rbind(tb_FLB, tb_Input)
tb_Total <- tb_Total[, sort(names(tb_Total))]

tb_Total

```

Create number of channels column.

```{r}
tb_Total <- tb_Total %>% 
  group_by(data_type) %>% 
  mutate(num_of_channels = sum(! is.na(Gain))) %>%
  ungroup()

# cheking
tb_Total %>% group_by(data_type) %>% summarise(unique(num_of_channels))
```

### Determine Pre-existing channels in Input

```{r}
pre_exsit_channels <- tb_Total %>%
  filter(data_type == "Input") %>%
  select(Gain, freq_num_id) %>%
  filter(!is.na(Gain)) %>%
  select(freq_num_id) %>%
  unlist() 

pre_exsit_channels

pr_exsit_ch_names <- str_c("g_", pre_exsit_channels, "_over")

pr_exsit_ch_names
```


# Plots

```{r}
# Plot Output power spectrum over channel n-th power with a small power gap between fully loaded band and input channel loading

which_to_plot <- 6
if(which_to_plot > length(pr_exsit_ch_names)) which_to_plot <- 1

ggplot(tb_Total, aes_string(y= pr_exsit_ch_names[which_to_plot], x = "Freq")) +
   geom_point(aes(color = data_type, shape = factor(num_of_channels)), size = 2) +
   labs(shape ='# of Channels') +
   labs(color ='Data') +
   ylab(str_c("Channel Power / Channel ", pre_exsit_channels[which_to_plot],"-th Power"))
```

If you run in Rstudio, you can uncomment and use the following code bellow to explore all input channels interactively (use settings sign in left top corner). 

```{r}
# library(manipulate)
# manipulate({
#   ggplot(tb_Total, aes_string(y= pr_exsit_ch_names[which_to_plot], x = "Freq")) +
#     geom_point(aes(color = data_type, shape = factor(num_of_channels)), size = 2) +
#     labs(shape ='# of Channels') +
#     labs(color ='Data') +
#     ylab(str_c("Channel Power / Channel ", pre_exsit_channels[which_to_plot],"-th Power"))
# }
#   , which_to_plot = slider(1, length(pr_exsit_ch_names)))
```

# Calculate recomended frequencies

### Avoiding repetitives

By stacking all pre-existing channel in "avoid_repetitives" tibble, we make sure the newly proposed channels are not repetitive.

```{r}
# define function helping to do this
compare_test <- function(tb_Total, load_data = "Full load", margin, v = 1) {
  myf = function(x){abs(x - v) < margin} # function to apply to filtering condition
  df_temp <- filter(tb_Total, data_type == load_data) %>%
    select(Freq, freq_num_id, freq_text_id,
           match(pr_exsit_ch_names, names(.))) %>% # selecting col with pre_exist_ch.
    mutate_each(funs(TF = myf),                    # applying margin condition
                -Freq, -freq_num_id, -freq_text_id) %>%
    # take only those rows, where all conditions are TRUE:
    filter(rowSums(.[, str_detect(names(.), "TF")]) == 
             sum(str_detect(names(.), "TF"))) %>% 
    select(-ends_with("TF"))
  
  df_temp
}
 
avoid_repetitives <- compare_test(tb_Total, load_data = "Full load", margin = 1, v = 1) %>%
  filter(! freq_text_id %in% str_c("g_", pre_exsit_channels) ) 
   
```

### Calculate zzz-s

```{r}
# num_wl_after_add parameter defines the number of wavelengths after add events
num_wl_after_add <- num_add_wl + length(pre_exsit_channels)

## zz1 defines the total number of possible combination to pick num_add_wl wavelenths out of 80 (excluing pre-existing wavelengths)
zz1 <-combn(avoid_repetitives[, pr_exsit_ch_names[1]] %>% unlist, 
            num_add_wl, simplify=F)

# zzz2 parameter gives the freq_text_id of the num_add_wl newly proposed channels. Type: zzz2[( k parameter value)]
zzz2 <-combn(avoid_repetitives$freq_text_id, num_add_wl, simplify=F)

###########Algorithm OUTCOMEs
# zzz4 parameter gives the num-id of the num_add_wl newly proposed channels. Type: zzz4[( k parameter value)]
zzz4 <-combn(avoid_repetitives$freq_num_id, num_add_wl, simplify=F)

# zzz3 parameter gives the frequencies of the num_add_wl newly proposed channels. This paprameter is the main OUTCOME of this algorithm. Type: zzz3[( k parameter value)]
zzz3 <-combn(avoid_repetitives$Freq, num_add_wl, simplify=F)
####################################################
```

### Go over all cases to calculate c and k

```{r calculate_c_k, cache=T}
############## Algorithm Core 
c <- 1
k <- 1

while(c <= length(zz1)){
  dff3 <- tb_Total %>%
    filter(
      data_type == "Full load",
      freq_num_id %in% as.numeric( c(pre_exsit_channels, zzz4[[k]] ) )) 
  
  condition_check_1 <- dff3 %>%
    select(match( pr_exsit_ch_names, names(.))) %>%
    summarize_each(funs( abs( sum(., na.rm = T)-num_wl_after_add) > m_new ) ) %>%
    unlist() %>%
    sum()

  condition_check_2 <- dff3 %>%
    select(match( str_c(zzz2[[k]], "_over"), names(.))) %>%
    filter(row_number() <= num_wl_after_add) %>%
    summarize_each(funs( abs( sum(., na.rm = T)-num_wl_after_add) > m_pre ) ) %>%
    unlist() %>%
    sum()
  
  # "OR" condition - at least 1 is True
  if (condition_check_1 + condition_check_2 >= 1){k <- k + 1}
  
  c <- c + 1
}

print(c)
print(k)
```

### The proposed frequencies

Based on calculations proposed frequencies are

```{r}
zzz3[k]
```

